IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-08 paper/retrofit.tex
Fix color in lambda_ES.

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
te   ::= tv | tx | te te | if te then te else te
       | ref te | !te | te := te | fix e
tE   ::= tHole | tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE | fix E

>>>>

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
te   ::= tv | tx | te te | if te then te else te
       | ref te | !te | te := te | fix te
tE   ::= tHole | tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE | fix tE
